DNSKEY Management

### 2012-12-04 paper/paper.tex
Introduction to ch. zone

\section{Case-Study: Switzerland (\texttt{ch.} Zone)\wbts}
\label{sec:case-study}

\paragraph{Certificate Chain} According to a query on
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
verifiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TAR is required.

>>>>

\section{Case-Study: \texttt{ch.} Zone\wbts}
\label{sec:case-study}

The \verb|ch.| zone is managed by SWITCH, the institution which also
employs the Swiss educational network. In this section we briefly
point out the current deployment status of DNSSEC and how SWITCH
handles the discussed key management issues.

\paragraph{Certificate Chain} According to a query on SecSpider
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
verifiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TAR is required.
